Breakable Elastic-plastic Constraint for\\Rigid Body Simulation

### 2017-10-01 pdocs/thesis/epj-jcgt.tex
work on jcgt article

\paragraph{Limitations}
Forces are calculated by dividing impulse by timestep and maximum impulse is calculated
by multiplying maximum force by timestep. 
This means that simulation of quick interactions requires small timestep.
This limitation is not introduced by this approach but is build in feature of impulse-based simulation.
Bending moment - normal force interactions and multiaxial stress are not taken into account. 
Basically these limitations just state that results from these simulations cannot not be used
for structural analysis.

@@

\paragraph{Plastic capacities}
In this work, plasticity is handled by defining maximum forces using plastic capacities, which are defined below.

@@

@@

\paragraph{Analysis of results}
Unexpected results is typical issue when new kind of structures are analyzed or new methods are are
used. In gaming results do not have to match real world results but main focus of implementations
in this work is to provide more realistic simulations.

@@

\subsection{Test cases}

>>>>

\paragraph{Limitations}
Forces are calculated by dividing impulse by timestep and maximum impulse is calculated
by multiplying maximum force by timestep. 
This means that simulation of quick interactions requires small timestep.
This limitation is not introduced by this approach but is build in feature of impulse-based simulation.
Bending moment - normal force interactions and multiaxial stress are not taken into account. 
Simulation of many bodies connected by constraints

@@

\paragraph{Plastic capacities based on dimensions and material}
In this work, plasticity is handled by defining maximum forces using plastic capacities, which are defined below.

@@

\paragraph{Plastic capacities based on desired behaviour}
Capacities can also be defined directly based on desired scenarios.
E.g. joints for bridge can designed so that maximum shear force is larger than
weight of heaviest vehicle so that all vehicles can drive to bridge. Maximum 
bending moment could be set so that joint will start to rotate when heaviest vehicle is
near the middle of bridge.

For elastic-plastic cases maximum capacity can also be defined by setting maximum elastic 
displacement or rotation.

@@

@@

\subsection{Examples}
